### 2021-06-22 README.Rmd
updated package for CRAN installation

<!-- badges: start -->
<!-- badges: end -->

@@

<!-- You can install the released version of the `fasano.franceschini.test` package from [CRAN](https://CRAN.R-project.org) with:

@@

And the --> 
You can install the development version of the `fasano.franceschini.test` package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nesscoder/fasano.franceschini.test")
```
## Example

>>>>

<!-- badges: start -->

`badge_custom(x = "arXiv", y = "abs/2106.10539", color = "yellow", url = "https://arxiv.org/abs/2106.10539")` 
[![R build status](https://github.com/nesscoder/fasano.franceschini.test/workflows/R-CMD-check/badge.svg)](https://github.com/nesscoder/fasano.franceschini.test/actions) 
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
`r badge_devel("nesscoder/fasano.franceschini.test", "blue")` 
`r badge_code_size("nesscoder/fasano.franceschini.test")`
`r badge_cran_download("fasano.franceschini.test", "grand-total", "blue")`

<!-- badges: end -->

@@

You can install the released version of the `fasano.franceschini.test` package from [CRAN](https://CRAN.R-project.org) with:

@@

And the development version of the `fasano.franceschini.test` package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nesscoder/fasano.franceschini.test")
```

## Example
